Modeling vertical-axis cross-flow turbine wakes

### 2015-08-12 paper.tex
Some rewrapping and reorganizing

\begin{figure}[ht]
    \includegraphics[width=0.9\textwidth]{figures/perf_bar_chart} \caption{Power
        (left) and drag (right) coefficient predictions from experiments and each
        numerical model.} \label{fig:perf-comp}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.95\textwidth]{figures/profiles} \caption{Mean velocity
	(left) and turbulence kinetic energy (right) profiles at $x/D=1$ from 2-D
	simulations, 3-D simulations ($z/H=0$), and experiments \cite{Bachant2015-JoT}.}
\label{fig:profiles}
\end{figure}

>>>>

    \includegraphics[width=0.9\textwidth]{figures/perf_bar_chart}

    \caption{Power (left) and drag (right) coefficient predictions from
        experiments and each numerical model.}

    \label{fig:perf-comp}
\end{figure}

@@

\begin{figure}
    \centering

    \includegraphics[width=0.95\textwidth]{figures/profiles}

    \caption{Mean velocity (left) and turbulence kinetic energy (right) profiles
        at $x/D=1$ from 2-D simulations, 3-D simulations ($z/H=0$), and experiments
        \cite{Bachant2015-JoT}.}

    \label{fig:profiles}
\end{figure}
